---
title: "Daycare Centers in El Paso Texas"
output: html_document
---

This project is aimed at having an easily accessable place for parents to find daycare centers and see the deficiencies found during inspections.

The only extra folder needed is a 'data' subfolder. 

Data is gathered from data.texas.gov and combined two datasets[^1]:

[DFPS CCL Daycare and Residential Operations Data](https://data.texas.gov/Social-Services/DFPS-CCL-Daycare-and-Residential-Operations-Data/bc5r-88dy) 

This dataset contains all the basic information for each daycare center. In this dataset the Operation_ID column is what ties it to the second dataset.

[DFPS CCL Inspection Investigation Assessment Data](https://data.texas.gov/Social-Services/DFPS-CCL-Inspection-Investigation-Assessment-Data/m5q4-3y3d) 

This dataset contains information about the results of inspections with detailed notes of any deficiencies found. 

## Packages
The following packages are used:

* Leaflet - development 
  + This is the maping package. 
* Leaflet.extras - developement. 
  + This is some extra plugins for Leaflet not included in the main package.
* Dplyr
  + This is used for the %>% function to work. (I think)

To install the developement packages run the following code. 

```{r}
devtools::install_github('rstudio/leaflet')
devtools::install_github('bhaskarvk/leaflet.extras')
```


Install the development versions of Leaflet for R and leaflet.extras. This is just to ensure that we have the most up-to-date plugins since Leaflet for R does not include all the plugins for Leaflet. 


To download the data used run the following code. Using the URL ensures that the data is current.

```{r}
URL <- "https://data.texas.gov/api/views/bc5r-88dy/rows.csv?accessType=DOWNLOAD"
download.file(URL, destfile = "./data/operation.csv", method="curl")
rm(URL)

URL <- "https://data.texas.gov/api/views/m5q4-3y3d/rows.csv?accessType=DOWNLOAD"
download.file(URL, destfile = "./data/investigation.csv", method="curl")
rm(URL)
```


Now that we have the files in our



[^1]: The data dictionaries which further describe the data can be found in the links as well. 